Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2018-05-21 writeup/response2reviews.tex

\documentclass[11pt]{letter}
\usepackage[hidelinks]{hyperref}
\usepackage[green]{msuletterhead}
\usepackage[usenames,dvipsnames]{xcolor}
\pagenumbering{gobble}

\newcommand{\gb}[1]{{\bf\color{black}{#1}}}
\newcommand{\plr}[1]{{\it\color{purple}{(#1)}}}
\newcommand{\gc}[1]{{\it\color{blue}{(#1)}}}

\begin{document}

Re-Submission Cover Letter \hfill	\today\\
\emph{Genetics}
\\\\\\
To the Editor,

Please find enclosed the re-submission of our manuscript, 
``Inferring Continuous and Discrete Population Genetic Structure Across Space,"
for re-consideration for publication in Genetics.

We appreciate the opportunity to submit a revised version of the manuscript.  
The comments provided by the Editor 
and the anonymous reviewer are very helpful, 
and we believe the manuscript is improved as a result 
of their critiques.

Our detailed responses to those comments are inset below (in bold), 
but, in brief, we have included more of the results of the ADMIXTURE analyses 
in the main body of the text.
Specifically, we have added figure panels to Figures 7 and 8 
that explicitly compare \texttt{conStruct}'s results with those of ADMIXTURE 
on the black bear dataset.
We have also added text throughout the results to increase the depth of 
our comparison of \texttt{conStruct} and ADMIXTURE.

@@

We hope that the paper is now acceptable for publication.\\\\
%

Thank you for your consideration,\\
Gideon Bradburd (for all of the authors).

\newpage

\textbf{Editor}\\
We received the previous reviews for your paper, and sent also sent it out to a new reviewer, along with your response to the earlier reviews. Both the new reviewer and I believe that you have answered the previous criticisms in a reasonable way, and I am pleased to tell you that your paper is potentially suitable for publication in GENETICS. However, the new reviewer did have several comments which you should consider in preparing the final version (see the end of this email). In particular, they suggest including more of the ADMIXTURE models in the main text. I think that this could be helpful, but would not insist on it.

\textbf{Reviewer}\\
\begin{itemize}
\item This manuscript presents a valuable model that addresses an long standing chestnut in population genetic analysis, which is how to jointly analyze discrete and spatially continuous variation within a single dataset.  The method presented does seem to be something of a breakthrough in addressing this problem sensibly.  I found the authors response to previous reviewer comments to be generally reasonable. However, I do think that there is a strong case for putting some more ADMIXTURE model results into the text and possibly for some additional analyses.

\item I agree with the authors point in their letter that ADMIXTURE/STRUCTURE is important because it is what almost everyone would do otherwise.  The key goal for the manuscript is to show that the method that everyone uses gives results that can be misleading/unhelpful and that the layered model is a substantial improvement. This is very clear for the simulated data. The previous reviewers are right to ask for additional simulations in the sense that a more biological simulation would make a stronger case for practical utility and it need not lengthen the manuscript significantly, since the current simulations could be largely relegated to supplementary material as representing "simulation according to the model". But this is definitely an optional, since there are presentational arguments to be made either way.

\item A more biological simulation is not necessary as long as the real data examples are convincing. For the Poplar data, the key insight of the model is that there are three well-supported layers in addition to isolation by distance. This is not clear according to ADMIXTURE, which gives continuous improvement for K, although the clustering itself is reasonable. The differences in patterns of IBD between populations are also interesting.

\item For the bear data, there is a stronger case to be made, namely that as well as estimating a biologically insightful number of layers, individual ADMIXTURE or non-spatial model components are positively misleading for K=3 or more. For the Poplar example, the results are not actively misleading , they just represent finer and finer geography. The misleadingness of the bear results can be shown by the fact that although the cross validation shows continuous improvement, the admixture components are highly inconsistent between runs. For example at K=3, a component is shown that is shared between East and West, which if interpreted literally would represent a biologically important result about connections between populations but the clustering of the yellow populations disappears entirely for K=4. Therefore, I think there is a good case to be made for showing the ADMIXTURE model results in the text and to discuss the misleading/ unstable nature of any particular result.

\item It would be interesting to do some kind of plot for ADMIXTURE results, to demonstrate that populations that share affinity according higher components are not particularly similar when allowing for geographical distance. This would be a rather direct way of showing that the ADMIXTURE model is not producing insightful results, despite the continuous improvement in model probability for higher K. In this context, I always think of the "clines vs clusters" paper by Rosenberg. It would be great to have some kind of figure to show that for K=2, it looks like clusters but for K=3, the clusters add much less.

\item The layer specific covariances show a very funny pattern, tending to infinity for low distances for components 3 and above for the bear data. I am not sure I understand this. Is this discussed anywhere?\\\\
\gb{I think what's happening is that these layer-specific covariances for layers $>$2 
are describing local departures from global patterns of IBD, 
as might be expected due to, e.g., inbreeding.
We have added some text to that effect in Lines XXX-XXX.}

\item Minor point, in figure 4, legend, should it read in each run of the spatial model, rather than nonspatial model?\\\\
\gb{Good catch!  Caption has been fixed.}
\end{itemize}

### 2018-05-21 writeup/conStruct.tex
reformatting for resub
resubmission for reals
submission to genetics
started edits for genetics reviews

%% added PLR
\newif\ifsubmissionversion
%\submissionversionfalse
\submissionversiontrue
\newif\ifincludesupplement
\includesupplementtrue
%\includesupplementfalse
\newif\iffloatsatend
\floatsatendfalse
%\floatsatendtrue
\newif\ifincludefigs
\includefigstrue
%\includefigsfalse
\newif\ifsuppmatfigs
\suppmatfigsfalse
%\suppmatfigstrue
\iffloatsatend
\usepackage[nomarkers]{endfloat}
\fi
%% end added PLR

@@

% line numbers
\usepackage[right]{lineno}

@@

% Header and Footer with logo
\usepackage{graphicx}
\ifsubmissionversion
    \usepackage{lastpage,fancyhdr}
    \usepackage{epstopdf}
    \pagestyle{myheadings}
    \pagestyle{fancy}
    \fancyhf{}
    \setlength{\headheight}{27.023pt}
    \lhead{\includegraphics[width=\textwidth]{latex/PLOS-submission.eps}}
    \rfoot{\thepage/\pageref{LastPage}}
    \renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
    \fancyheadoffset[L]{2.25in}
    \fancyfootoffset[L]{2.25in}
    \lfoot{\sf PLOS}
\fi

@@

\begin{figure}
	\centering
	\ifincludefigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_laycon_barplots.pdf}}
	\fi
		\caption{
            Results for data simulated using $K=1$, showing
            layer/cluster contributions (i.e., how much each layer/cluster contributes to total covariance),
            from \texttt{conStruct} runs using $K = 1$ through 7 
			for the spatial model (left), and the nonspatial model (right).
			In each run of the nonspatial model, a single layer explained nearly all the covariance
            (additional bars are present but not visible).
		}\label{simK1_laycon}
\end{figure}

@@

Both nonspatial \texttt{conStruct} and ADMIXTURE displayed 
the successive partitioning of space and the clines of admixture seen in the simulation results.
The details of each were somewhat different 
(Fig \ref{populus_nsp_pies} vs. Fig \ref{populus_admixture}), 
and also differed across the replicate analyses, 
but each strongly favored the most cluster-rich model
(Figs \ref{populus_xvals} and \ref{poplar_admix_CVerrors}).

@@

The spatial models have strong statistical support 
up until around $K=5$ or 6 (Fig \ref{bear_xvals}),
but additional spatial layers beyond $K=2$ contribute little to total covariance (Fig \ref{bear_laycon}).
The locations of admixed individuals 
are consistent with a scenario of postglacial expansion from two refugia, 
one in the American Southwest and one in the American Southeast, 
meeting near the Northwest coast of North America and the Cascade Range.
However, lack of any samples from Canada and Mexico, 
and lack of denser sampling across northern North America, 
make more detailed interpretations untrustworthy.

@@

\section*{Supplementary Information}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
%
% \linespread{1}
% \iffloatsatend
% \processdelayedfloats
% \fi
%
\ifsuppmatfigs
	\clearpage
\fi
\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_sp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a spatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_sp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a spatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_sp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a spatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_adprop_fit.pdf}}
	\fi
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=2$.
		}\label{simK2_adprop_fit}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_adprop_fit.pdf}}
	\fi
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=3$.
		}\label{simK3_adprop_fit}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_nsp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a nonspatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_nsp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a nonspatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_nsp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a nonspatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/admixture_simK1_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using ADMIXTURE \cite{ADMIXTURE} for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
	The model with the lowest cross-validation error (i.e., the preferred model) was $K=7$.
    }\label{admix_simK1}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/admixture_simK2_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using ADMIXTURE \cite{ADMIXTURE} for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
	The model with the lowest cross-validation error (i.e., the preferred model) was $K=7$.
    }\label{admix_simK2}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/admixture_simK3_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using ADMIXTURE \cite{ADMIXTURE} for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
	The model with the lowest cross-validation error (i.e., the preferred model) was $K=7$.
    }\label{admix_simK3}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_std_xval.pdf}}
	\fi
		\caption{
			Cross-validation results for data simulated under $K=1$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK1_xval}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_std_xval.pdf}}
	\fi
		\caption{
			Cross-validation results for data simulated under $K=2$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK2_xval}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_std_xval.pdf}}
	\fi
		\caption{
			Cross-validation results for data simulated under $K=3$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK3_xval}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/sims_CVerror.pdf}}
	\fi
	\caption{
	ADMIXTURE cross-validation results for data simulated under $K=1$, $K=2$, and $K=3$, 
	run with $K=1$ through 7 using 50 data folds (\texttt{--cv=50}).  
	The inset plots zoom in on cross-validation results outlined in the dotted boxes.
	The preferred model (with the lowest cross-validation error) is highlighted with an asterisk.
    }\label{sim_admix_CVerrors}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_laycon_barplots.pdf}}
	\fi
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial \texttt{conStruct} model (right).
			Data were simulated using $K=2$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK2_laycon}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_laycon_barplots.pdf}}
	\fi
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial \texttt{conStruct} model (right).
			Data were simulated using $K=3$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK3_laycon}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_sampling_map.pdf}}
	\fi
	\caption{
	Map of the sampled \textit{Populus} populations included in the analysis.
	The color of the sampling location denotes the putative species.
    }\label{populus_map}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_sp_pies.pdf}}
	\fi
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial \texttt{conStruct} model for $K=2$ through 7.
    }\label{populus_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_nsp_pies.pdf}}
	\fi
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the nonspatial \texttt{conStruct} model for $K=2$ through 7.
    }\label{populus_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!p]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_sp_layer_covs.pdf}}
	\fi
	\caption{
	Plots showing the layer-specific parametric covariance curves
	estimated for the \textit{Populus} data using 
	the spatial \texttt{conStruct} model run with $K=1$ through 6.
	Line colors are consistent with layer colors in Fig \ref{populus_sp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \bals{} and \tri{};
	green on green points are sample covariances between \tri{} and \tri{}.
    }\label{populus_sp_layer_covs}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

>>>>

%% added PLR
\newif\ifsubmissionversion
\submissionversionfalse
%\submissionversiontrue
\newif\ifincludesupplement
\includesupplementtrue
%\includesupplementfalse
\newif\iffloatsatend
\floatsatendfalse
%\floatsatendtrue
\newif\ifincludefigs
\includefigstrue
%\includefigsfalse
\newif\ifsuppmatfigs
%\suppmatfigsfalse
\suppmatfigstrue
\newif\iflinenos
\linenostrue
%\linenosfalse

\iffloatsatend
\usepackage[nomarkers]{endfloat}
\fi
%% end added PLR

@@

% line numbers
\usepackage[right]{lineno}
\iflinenos
\linenumbers
\fi

@@

% Header and Footer with logo
\usepackage{graphicx}
\ifsubmissionversion
    \usepackage{lastpage,fancyhdr}
    \usepackage{epstopdf}
    \pagestyle{myheadings}
    \pagestyle{fancy}
    \fancyhf{}
    \setlength{\headheight}{27.023pt}
%    \lhead{\includegraphics[width=\textwidth]{latex/PLOS-submission.eps}}
    \rfoot{\thepage/\pageref{LastPage}}
    \renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
    \fancyheadoffset[L]{2.25in}
    \fancyfootoffset[L]{2.25in}
%    \lfoot{\sf PLOS}
\fi

@@

\begin{figure}
	\centering
	\ifincludefigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_laycon_barplots.pdf}}
	\fi
		\caption{
            Results for data simulated using $K=1$, showing
            layer/cluster contributions (i.e., how much each layer/cluster contributes to total covariance),
            from \texttt{conStruct} runs using $K = 1$ through 7 
			for the spatial model (left), and the nonspatial model (right).
			In each run of the spatial model, a single layer explained nearly all the covariance
            (additional bars are present but not visible).
		}\label{simK1_laycon}
\end{figure}

@@

\paragraph{Comparison to ADMIXTURE}
Both nonspatial \texttt{conStruct} and ADMIXTURE displayed 
the successive partitioning of space and the clines of admixture seen in the simulation results.
The details of each were somewhat different 
(Fig \ref{populus_nsp_pies} vs. Fig \ref{populus_admixture}), 
and also differed across the replicate analyses.
These differences between runs and methods may be due to 
noise in the different inference algorithms employed,
multi-modality in the likelihood surfaces, or 
to differences in the specifics of model 
(e.g., the priors used in nonspatial \texttt{conStruct}, 
or the fact that ADMIXTURE is modeling each allele's frequency in each cluster, 
rather than the covariance across all alleles).
However, overall, the behavior of both methods is quite similar: 
each recovers the \tri{}/\bals{} split with the first two clusters modeled, 
then, with higher values of $K$, 
uses subsequent clusters to subdivide the \tri{} samples 
into geographically restricted foci of cluster membership.
And, both nonspatial \texttt{conStruct} and ADMIXTURE 
strongly favored the most cluster-rich model
(Figs \ref{populus_xvals} and \ref{poplar_admix_CVerrors}).

@@

The spatial models have strong statistical support 
up until around $K=5$ or 6 (Fig \ref{bear_xvals}),
but additional spatial layers beyond $K=2$ contribute little to total covariance (Fig \ref{bear_laycon}).
The locations of admixed individuals 
are consistent with a scenario of postglacial expansion from two refugia, 
one in the American Southwest and one in the American Southeast, 
meeting near the Northwest coast of North America and the Cascade Range.
However, lack of any samples from Canada and Mexico, 
and lack of denser sampling across northern North America, 
make more detailed interpretations untrustworthy.
The spatial covariance functions estimated in layers beyond the first two 
take very large values over small spatial lags, 
but decay sharply after that.
This feature, combined with the overall amounts 
and spatial patterns of ancestry in those layers, 
suggests that these layers are describing processes 
that shape genetic variation at local scales, such as inbreeding, 
which affects covariance between individuals within demes, 
but has limited impact on covariance between demes.

@@

\section*{Supplementary Information}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
%
% \linespread{1}
% \iffloatsatend
% \processdelayedfloats
% \fi
%
\ifsuppmatfigs
	\clearpage
\fi
\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_sp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a spatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_sp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a spatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_sp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a spatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_adprop_fit.pdf}}
	\fi
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=2$.
		}\label{simK2_adprop_fit}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_adprop_fit.pdf}}
	\fi
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=3$.
		}\label{simK3_adprop_fit}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_nsp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a nonspatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_nsp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a nonspatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_nsp_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using a nonspatial \texttt{conStruct} model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/admixture_simK1_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using ADMIXTURE \cite{ADMIXTURE} for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
	The model with the lowest cross-validation error (i.e., the preferred model) was $K=7$.
    }\label{admix_simK1}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/admixture_simK2_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using ADMIXTURE \cite{ADMIXTURE} for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
	The model with the lowest cross-validation error (i.e., the preferred model) was $K=7$.
    }\label{admix_simK2}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/admixture_simK3_pies.pdf}}
	\fi
	\caption{
	Map of admixture proportions estimated using ADMIXTURE \cite{ADMIXTURE} for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
	The model with the lowest cross-validation error (i.e., the preferred model) was $K=7$.
    }\label{admix_simK3}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK1_std_xval.pdf}}
	\fi
		\caption{
			Cross-validation results for data simulated under $K=1$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK1_xval}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_std_xval.pdf}}
	\fi
		\caption{
			Cross-validation results for data simulated under $K=2$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK2_xval}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_std_xval.pdf}}
	\fi
		\caption{
			Cross-validation results for data simulated under $K=3$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK3_xval}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/admixture/sims_CVerror.pdf}}
	\fi
	\caption{
	ADMIXTURE cross-validation results for data simulated under $K=1$, $K=2$, and $K=3$, 
	run with $K=1$ through 7 using 50 data folds (\texttt{--cv=50}).  
	The inset plots zoom in on cross-validation results outlined in the dotted boxes.
	The preferred model (with the lowest cross-validation error) is highlighted with an asterisk.
    }\label{sim_admix_CVerrors}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK2_laycon_barplots.pdf}}
	\fi
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial \texttt{conStruct} model (right).
			Data were simulated using $K=2$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK2_laycon}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/sims/simK3_laycon_barplots.pdf}}
	\fi
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial \texttt{conStruct} model (right).
			Data were simulated using $K=3$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK3_laycon}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_sampling_map.pdf}}
	\fi
	\caption{
	Map of the sampled \textit{Populus} populations included in the analysis.
	The color of the sampling location denotes the putative species.
    }\label{populus_map}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_sp_pies.pdf}}
	\fi
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial \texttt{conStruct} model for $K=2$ through 7.
    }\label{populus_sp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_nsp_pies.pdf}}
	\fi
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the nonspatial \texttt{conStruct} model for $K=2$ through 7.
    }\label{populus_nsp_pies}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_sp_layer_covs.pdf}}
	\fi
	\caption{
	Plots showing the layer-specific parametric covariance curves
	estimated for the \textit{Populus} data using 
	the spatial \texttt{conStruct} model run with $K=1$ through 6.
	Line colors are consistent with layer colors in Fig \ref{populus_sp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \bals{} and \tri{};
	green on green points are sample covariances between \tri{} and \tri{}.
    }\label{populus_sp_layer_covs}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi

\begin{figure}[!ht]
	\centering
	\ifsuppmatfigs
		{\includegraphics[width=\textwidth]{figs/populus/populus_nsp_layer_covs.pdf}}
	\fi
	\caption{
	Plots showing the cluster-specific parametric covariances 
	estimated for the \textit{Populus} data using 
	the nonspatial \texttt{conStruct} model run with $K=1$ through 6.
	Line colors are consistent with cluster colors in Fig \ref{populus_nsp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \bals{} and \tri{};
	green on green points are sample covariances between \tri{} and \tri{}.
    }\label{populus_nsp_layer_covs}
\end{figure}
\ifsuppmatfigs
	\clearpage
\fi
